%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
% \geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}
% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\name{Kevin}{Schoonover}
% \position{Software Engineer}
% \address{246-1002, Gwangmyeongmayrouge Apt. 86, Cheongna lime-ro, Seo-gu, Incheon-si, 404-180, Rep. of KOREA}

\mobile{(214) 499-7919} 
\email{schoonoverkevinm@gmail.com}
% \homepage{}
\github{kevinschoonover}
\linkedin{schoonoverkevinm}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

% \quote{``Must be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Campus Recruitment Team}
  {Reddit}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
% \lettertitle{Job Application for Software Engineering Inter}
% How the letter is opened
\letteropening{Dear Sir or Madam,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Kevin Schoonover~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{You can add any feature to Reddit. What would you add and why?}
Reddit's feature set provides powerful and fast ways to consume a large number of
posts in order to find funny gifs, interesting articles, my favorite car
salesman memes, and any other content a user could want. But, what if users did not
need to consume large amounts of posts to find the information they want? As the
6th most popular site, Reddit has access to a large amount of data which can be
used to personalize this experience more closely. I would add a `personalized'
sort option to the `popular' section which will take the users subscribed
subreddits, comment history, viewing history, upvotes/downvotes, and other
metrics to determine new subreddits and posts the user would like. The `Best' sort
filter in the `Home' tab provides a similar experience, but focuses on `
surfacing posts that are from communities you’ve shown interest in recently'
(\url{https://www.reddit.com/r/changelog/comments/7hkvjn/what_we_think_about_when_we_think_about_ranking/}).
Reddit should take this idea further and attempt to match a user with a new
subreddit and show them a new post they have not considered before. The suggestion
has a couple of problems: how does Reddit ensure with a high accuracy these are
posts the user wants to see and how to prevent an echo chamber of information
and ideas that usually ensues with personalized information. Both problems can
be solved primarily by making it optional as a filter. The user, in this case,
can enable and disable the feature as needed and come back at a later time if
the system does not have enough data to make accurate predictions. Other
concerns such as privacy and more specific implementation to solve the
problems require a much longer discussion.

\lettersection{What is Captain Kevin's first Galactic Reddit Academy mission?}
`Ladies and Gentleman, plot a course for the center of the Milky Way Galaxy,` I
say as I walk into the bridge and sit in my DXRacer themed captain's chair, `we
are going to see a supermassive black hole!'. I think supermassive black holes
are incredibly interesting and visually stunning. Both the object and the song
by Muse tantalize my imagination with their sophisticated fundamentals. Our
expedition would be one to satisfy my desire to see the event horizon with my
own eyes and one of scientific exploration. Special relativity and its space and
time components are stretched to their limits because of the infinite warping
that black holes create. I have spent many hours watching YouTube videos to gain
an intuition on how space and time form this underlying plane to our universe
while showing the limits of Newtonian Gravity. The trek only reinforced my lack
of understanding, but a trip to see a black hole may solve this curiosity. The
last, selfish reason is the bragging rights of being the first person to see a
black hole with my own eyes.  While this trip will take 26,490 $\pm$ 100 light
years, it would be well worth it to see how the beauty of an event horizon and
the underlying science meet.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}

