%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Software Engineering Intern @ Azure Networking} % Job title
  {Microsoft} % Organization
  {Redmond, Washington} % Location
  {May 2019 - Aug. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created a data pipeline to aid Microsoft's future traffic
             engineering and to verify routing policy correctness. The pipeline
             processes 9 TiB of BGP Monitoring Protocol (BMP) data daily in 1.5 hours
             into a routing table snapshot of Azure's WAN using Microsoft's internal
             map-reduce framework.}
      \item{Detected and mitigated at-risk BGP-based incidents on Azure's WAN,
            which may have caused outages preventing certain customer traffic from
            entering Microsoft, by developing automated unit-tests on the BMP routing
            snapshot.}
    \end{cvitems}
  }


\cventry
  {Software Engineering Intern} % Job title
  {Garmin International} % Organization
  {Olathe, Kansas} % Location
  {May 2018 - Aug. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Utilized the Jinja2 templating engine (Python) to autogenerate
        thousands of aviation display library C module tests for FAA
        compliance.}
      \item {Developed a documentation generation tool with pylatex (Python) to
        automatically document widgets in the ARINC 661 aviation platform.}
      \item {Performed code reviews to ensure compliance with C best practice
        and internal coding standards while verifying requirement-based behavior.}
      % \item {Implemented boilerplate Garmin Touch Controller (GTC) page in C.}
    \end{cvitems}
  }

%---------------------------------------------------------

%\cventry
%  {Student Intern - Center for Cyber Defenders} % Job title
%  {Sandia National Laboratories} % Organization
%  {Livermore, CA} % Location
%  {May 2017 - Aug. 2017} % Date(s)
%  {
%    \begin{cvitems} % Description(s) of tasks/responsibilities
%      \item {Optimized an internal job processing queue for malware analysis by
%        replacing a legacy system with a Flask REST API (Python).}
%      \item {Utilized scikit-learn and hdbscan (Python) to cluster network data
%        to identify cyber-attack campaigns on government networks.}
%    \end{cvitems}
%  }

%---------------------------------------------------------

\cventry
  {Infrastructure Team Lead} % Job title
  {CEADS-LIN: Artificial Intelligence and Cybersecurity Research - Dr. Daniel Tauritz} % Organization
  {Rolla, MO} % Location
  {Jan. 2018 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Oversaw a team of 3 developers to add LXD containerization
        capabilities and scaling improvements to the network emulation framework
        Galaxy.}
      \item {Reviewed all developer's code to ensure comprehensive
        documentation, readability, performance, and proper functionality.}
    \end{cvitems}
  }

\cventry
  {Research Assistant} % Job title
  {} % Organization
  {} % Location
  {Jan. 2017- Jan. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed the network emulation framework Galaxy leveraging virtual
        machines (KVM), a Flask REST API (Python), PostgreSQL database, and
        AMQP-based communication to support high-volume experimentation of
        evolutionary agents in high-fidelity network topologies.}
      \item {Distributed Galaxy across 6 physical hosts using Ansible playbooks
        to decrease experiment time from weeks to days.}
      % \item {Programmed abstractions for the paramiko SSH library (Python) for
      %   evolutionary agents to send interactive commands to remote machines.}
    \end{cvitems}
  }

%---------------------------------------------------------

\cventry
  {President} % Job title
  {Missouri S\&T - Association of Computing Machinery (ACM)} % Organization
  {Rolla, MO} % Location
  {May 2018- Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Raised \$11,500 in total corporate sponsorship to fund existing and
             develop new talks and events for 120+ ACM members and 600+ students.}
      \item {Worked with 2 officers to re-brand the entire organization
             with a new UI design language, logos, and promotional materials.}
    \end{cvitems}
  }

\cventry
  {Co-Founder, Chair @ ACM Web} % Job title
  {} % Organization
  {} % Location
  {Dec. 2016 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Supervised all technical and design work for 6 developers
             redesigning \url{https://acm.mst.edu} using TypeScript, React,
             NodeJS, and GraphQL to automate tasks ACM was performing
             manually.}
      \item {Developed a TypeScript GraphQL API for processing user payments
             with Stripe and authenticating users with auth0.}
       \item {Implemented a resume portal for students and companies to upload resumes
              and view student resumes, respectively.}
    \end{cvitems}
  }

%---------------------------------------------------------

%\cventry
%  {Owner and Developer} % Job title
%  {Downfall Gaming} % Organization
%  {O'Fallon, MO} % Location
%  {May 2015 - Aug. 2016} % Date(s)
%  {
%    \begin{cvitems} % Description(s) of tasks/responsibilities
%			\item {Established the online gaming community known as Downfall Gaming in the game Garry’s Mod.}
%			\item {Instituted rules and policy to facilitate an enjoyable environment for all users who participated on the server.}
%			\item {Supervised a staff of 5 to ensure proper administration and compliance to server policy.}
%			\item {Programmed a variety of add-ons to the gaming server and webserver using GLua, MySQL, PHP, CSS, and HTML.}
%			\item {Optimized the expenses of the server while increasing performance, stability, and interactivity.}
%    \end{cvitems}
%  }

%---------------------------------------------------------

\end{cventries}
